Verification of Stencil Computations through Spatial Specifications

### 2016-07-04 paper.tex
related work: Blom 2014, Solar-Lezama 2007, and Tang 2011.

In an alternate approach,~\citet{abe2013model}

@@

>>>>

% Abe, 2013, Model checking stencil computations
% -- Unable to obtain copy
% In an alternate approach,~\citet{Abe:2013:IPDPSW}

@@

% GPGPU
This work shares some similarities with efforts to verify kernels
written for General-Purpose Graphics Processing Unit (GPGPU)
programming, such as in \citet{Blom:2014:SoCP}. Stencils are a form of
kernel, and GPGPU programming can be viewed as a massively parallel
method of transforming a large matrix. However, that work focuses
mainly on the synchronisation of such kernels, and the avoidance of
data races, while we are interested in the correctness of stencils
embedded within a more typical general-purpose programming language.

% Sketching Stencils
\citet{Solar-Lezama:2007:PLDI} give specifications of stencils using
unoptimised ``reference'' stencils, coupled with partial
implementations of stencils, which are then completed by a code
generation tool. These kinds of specifications are just simple
implementations, so this tool is useful for hand-written, optimised
stencils. The primary purpose of this tool is optimisation rather than
correctness, and the language of specification is much different and
more elaborate than we envision for our system.

% Pochoir
\citet{Tang:2011:SPAA} defines a specification language for writing
stencils embedded in C++ (with Cilk extensions) that are then compiled
into fast parallel programs based on trapezoidal decompositions with
hyperspace cuts. The Pochoir specification language is used for
describing the computing kernel, boundary conditions and shape of the
stencil. Programs are first compiled in C++ with a template library
that checks whether the annotations are used correctly, and then a
Pochoir preprocessor may be applied to generate the high-performance
parallel version that takes advantage of the Cilk compiler.  Pochoir
is aimed primarily at assisting programmers who may be reluctant to
implement the tricky cache-oblivious ``hypertrapezoidal'' algorithms
that are significantly faster than the typical looping implementations
of stencil computations.

% 3D stencil codes
\citet{Zhang:2012:CGO}

% Ypnos
\citet{Orchard:2010:DAMP}
